---
name: Sara  
surname: Acevedo
position: "PhD student"
address: "Santiago, Chile"
phone: +56 9 576 50 773
www: saryace.github.io
email: "seaceved@uc.cl"
twitter: saryace
github: Saryace
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
library(vitae)
library(kableExtra)
library(tinytex)
```

# \faIcon{female} About me

* I am currently finishing my PhD in Engineering Sciences. 
* My research is gathering data from soil science and environmental studies, to derive statistical analysis and predictive models. 
* I teach introductory data science classes using R. 

# \faIcon{university} Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD (c) Engineering Sciences", "2016-2022", "Pontificia Universidad Católica de Chile", "Santiago, Chile",
  "Master of Science, Soil and Biogeochemistry", "2012-2014", "University of California-Davis", "Davis, USA",
  "Chemist, Environmental and Analytics specialization", "2003-2009", "Pontificia Universidad Católica de Chile", "Santiago, Chile"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# \faIcon{briefcase} Work

```{r}
tribble(
  ~Year, ~Type, ~Desc,
    "2022", "Education", "Course Facilitator: Introduction to Tidyverse for Data Science at Estacion Lastarria",
  "2020 - 2021", "Education", "Course maintainer MOOCs Coursera UC: Intro to programming (Python) and University training and learning",
  "2018 - 2020", "Education", "TA Environmental Biophysics at Pontificia Universidad Católica de Chile",
  "2018 - 2019", "Research", "Project evaluation focused on soil physical properties and environmental baselines for water treatment facilities at Desalsolar"
) %>% 
  detailed_entries(Type,Year,Desc)
```
\newpage


# \faIcon{hammer} Tools

* \faIcon{desktop} Programming:
  * R -- Python (basic)
* \faIcon{desktop} Software:
  * Rstudio -- ArcGis (basic) -- Zotero -- Hydrus 1-D
* \faIcon{calculator} Statistics
  * Modelation (linear models and machine-learning)
* \faIcon{thermometer-three-quarters} Environmental analysis
  * Analysis and interpretation of water and soil quality data.
  * Soil physics (infiltration, water balance and laboratory techniques)
* \faIcon{cogs} Others:
  * Advanced English -- Git/Github (basic) -- Markdown (RMarkdown y Github-flavored)

# \faIcon{file} Selected publications

## For the complete list, see my profile at [ORCID](https://orcid.org/0000-0003-3203-2106) \faIcon{mouse} or [Google Scholar](https://scholar.google.com/citations?user=WJqqnIQAAAAJ&hl=es) \faIcon{mouse}

```{r}
tribble(
  ~ article, ~ Year, ~ journal, ~ autores,
  "A comparative study of soil metal concentrations in Chilean urban parks using four pollution indexes", "2022", "Applied Geochemistry", "Alejandra S.Vega, Guillermo Arce, Javier I.Rivera, Sara E.Acevedo, SoniaReyes-Paecke, Carlos A. Bonilla, Pablo Pastén",
  "Unveiling soil temperature reached during a wildfire event using ex-post chemical and hydraulic soil analysis", "2022", "Science of The Total Environment", "Sofía I.Martínez, Cristina P.Contreras, Sara E.Acevedo, Carlos A.Bonilla",
  "Testing the integral suspension pressure method for soil particle size analysis across a range of soil organic matter contents", "2021", "International Agrophysics", "Sara E. Acevedo, Cristina P. Contreras, Carlos J. Ávila 1, Carlos A. Bonilla"
) %>% 
  detailed_entries(article,Year,journal,autores)
```

# \faIcon{medal} Distinctions

* Scholarship  ANID Doctorado Nacional 2016 (PhD)
* Scholarship ANID / Becas Chile 2012 (Master)

# \faIcon{heart} Volunteering

* Proud to be a part of [R-Ladies Chile since 2018](https://vimeo.com/rladieschile)  \faIcon{mouse}
* Colaborating with [Soil Biophysics Lab UC](https://www.youtube.com/channel/UCtpWXCy2NDEWpdeGLoyHmBg) \faIcon{mouse}

# \faIcon{comment} References

* Dr. Manuel Bugueño: CEO Desalsolar SPA \faIcon{mail-bulk} buguenomanuel at gmail.com 
* Dra. Alejandra Vega: Postdoc CEDEUS \faIcon{mail-bulk} asvega at uc.cl
* Dr. Carlos Bonilla: Thesis Supervisor \faIcon{mail-bulk} cbonilla at ing.puc.cl

